### 2018-04-17 paper/algorithm.tex
Fixes more Syntastic warnings

\newcommand{\localoverlay}{Squad Overlay}
\newcommand{\globaloverlay}{Global Overlay}

@@

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in \cref{file 
  exchange}

\subsection{The \localoverlay}%
\label{local overlay}

@@

\subsection{The \globaloverlay}%
\label{global overlay}

@@

Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
\begin{enumerate}
  \item Providing routing information to nodes during file exchange. This is 
    discussed in-depth in \cref{file exchange};
	\item Listing online devices and their probability of being online next time step.
\end{enumerate}

@@

\subsection{The file exchange}%
\label{file exchange}

@@

The device that contains Alice's file \commentAL{I don't like that dependence on the file's location} creates routes to several Introductory Points (IP), chosen at random among connected peers.
Alice uploads the addresses of her IP to the DHT at the position $k$.
One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
Bob fetches the addresses of Alice's IP from the DHT.
Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
The IP nodes forward the packet to Alice's device. 
Alice chunks her file into pieces of a predefined size, encrypted using $ek$.

@@

In the following equation, $S(sk,\texttt{message})$ means that $\texttt{message}$ is encrypted with the symmetric key $sk$, while $P(pk, \texttt{message})$ means that $\texttt{message}$ is encrypted using the public key $pk$.
Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:

$$ P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, R_{i+1}) $$

>>>>

\newcommand{\localoverlay}{Squad Overlay\xspace}
\newcommand{\globaloverlay}{Global Overlay\xspace}

@@

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local-overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in \cref{file 
  exchange}

\subsection{The \localoverlay}%
\label{local-overlay}

@@

\subsection{The \globaloverlay}%
\label{global-overlay}

@@

Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
\begin{enumerate}
  \item Providing routing information to nodes during file exchange. This is 
    discussed in-depth in \cref{file-exchange};
	\item Listing online devices and their probability of being online next time step.
\end{enumerate}

@@

\subsection{The file exchange}%
\label{file-exchange}

@@

The device that contains Alice's file \commentAL{I don't like that dependence on the file's location} creates routes to several Introductory Points (IP), chosen at random among connected peers.
Alice uploads the addresses of her IP to the DHT at the position $k$.
One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
Bob fetches the addresses of Alice's IP from the \ac{DHT}.
Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
The IP nodes forward the packet to Alice's device. 
Alice chunks her file into pieces of a predefined size, encrypted using $ek$.

@@

In the following equation, $S(sk,\texttt{message})$ means that $\texttt{message}$ is encrypted with the symmetric key $sk$, while $P(pk, \texttt{message})$ means that $\texttt{message}$ is encrypted using the public key $pk$.
Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:
\[
  P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, 
  R_{i+1})
\]
